---
title: "multicutoffRD"
output: rmdformats::readthedown
vignette: >
  %\VignetteIndexEntry{multicutoffRD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
# css: custom.css # Change colors of theme
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Description

The package `multicutofRD` is...

```{r setup, eval = FALSE}
install_github("PrincipitoAce/multicutoffRD")
library(multicutoffRD)
```

## optimalcutoffs()

Produces a data frame of new, optimal cutoff values alongside original cutoff values.

* Arguments
  + `X`: Uni-variate running variable
  + `Y`: Outcome variable
  + `C`: A vector of cutoff values
  + `c.vec`: A vector of BASELINE cutoff values
  + `K`: Folds
  + `kk`: Multiplicative factor on the smoothness parameter, set cost = 0 when varying kk
  + `cost`: Cost value

```{r, eval=FALSE}
cutoffs <- optimalcutoffs(X=X, Y=Y, C=C, c.vec=c.vec, K=20, kk=1, cost=0)
```

## cutoffsviz()

Produces a scatter plot of new and old cutoff values.

* Arguments
  + `data`: A data frame with the following values: original cutoff values (Original Cutoffs), new cutoff values (New Cutoffs), & the difference between the original and new cutoff values (Difference)
  + `color`: A palette of 2 colors

```{r, eval=FALSE}
cutoffsviz(cutoffs, color = c("red", "blue"))
```

[NOT DONE: Image of graph]

## Packages

The following packages were used to build this package:
  
* [dplyr](https://dplyr.tidyverse.org/)
* [haven](https://haven.tidyverse.org/)
* [nprobust](https://nppackages.github.io/nprobust/)
* [nnet](https://cran.r-project.org/web/packages/nnet/nnet.pdf)
* [tidyr](https://tidyr.tidyverse.org/)
* [ggplot2](https://ggplot2.tidyverse.org/)

## Repository

The repository for this package can be found at [`https://github.com/PrincipitoAce/multicutoffRD`](https://github.com/PrincipitoAce/multicutoffRD).


## References

* Zhang, Y., Ben-Michael, E., and Imai, K. (2023). [Safe Policy Learning under Regression Discontinuity
Designs with Multiple Cutoffs](https://arxiv.org/pdf/2208.13323.pdf).
